GO Enrichment
-------------

```{r}
library(goseq)
library(GO.db)
```

Making the table
-----------------

###File Input
Input the output from DE analysis.  This is made for a list that includes only the significant genes.  

```{r}
sigOnly <- read.csv("tf2cmbr_wtcmbr_DE1_sigonly.csv")
head(sigOnly)
dim(sigOnly)
colnames(sigOnly)
```

###Subset 
First I need to subset the list to up or down regulated, then add a new colum that specififys 1.  This column is need to for merging. 

```{r}
upITAG <- subset(sigOnly, logFC > 0, select = c(itag))
upITAG$up <- 1 
    
downITAG <- subset(sigOnly, logFC < 0, select = c(itag))
downITAG$down <- 1 
  
allITAG <- subset(sigOnly, select = c(itag))
allITAG$all <- 1
```

###Merge I - with normalized ITAG length gene list

read in guide. 
```{r}
geneLength <- read.csv("normalized_genes_length.csv")
head(geneLength)
#isolate just the gene list
genes <- subset(geneLength, select = c(itag))
```

First merge each table to geneLength
```{r}
upITAGmerge <- merge(genes, upITAG, by = "itag", all= TRUE)
dim(upITAGmerge)
downITAGmerge <- merge(genes, downITAG, by = "itag", all= TRUE)
dim(downITAGmerge)
allITAGmerge <- merge(genes, allITAG, by = "itag", all= TRUE)
dim(allITAGmerge)
```

head(allITAGmerge)

###Merge II - Merge them all together.

```{r}
matrixGOupdown <- merge(upITAGmerge, downITAGmerge, by = "itag", all = TRUE)
head(matrixGOupdown)
matrixGOupdownall <- merge(matrixGOupdown, allITAG, by = "itag", all = TRUE)
head(matrixGOupdownall)
matrixGO <- merge(matrixGOupdownall, geneLength, by = "itag", all = TRUE)
head(matrixGO)
```

###Clean Up
```{r}
matrixGO[is.na(matrixGO)] <- 0
head(matrixGO)
```

This is if you want to write out the table. 
write.table(matrixGO, "mydata.txt", sep="\t", quote= FALSE)

Ashishes section
-----------------

The is the input of the GOslim categories.  There are only two columns 1. itag and 2. go

```{r}
pat <- matrixGO#read.table("mydata.txt",header=TRUE)
head(pat)
cate <- read.table("melted.GOTable.txt",header=TRUE)
head(cate)
```

###Subseting for GO analysis

Specify the column you are interested in `pat$all` refers to all the DE gene regardless if they are up or down regulated. If you want to specify down regulated, specify `pat$down`.

```{r}
genes = as.integer(pat$all)
names(genes) = pat$itag
table(genes)
length(genes)

pwf = nullp(genes,bias.data=pat$length)

GO.wall = goseq(pwf,gene2cat = cate)
GO.wall
```

Here is where you can specify the p-value cut-off

```{r}
enriched.GO = GO.wall$category[p.adjust(GO.wall$over_represented_pvalue, method = "BH") < 0.05]

enriched.GO

my.GO <- as.character(enriched.GO)
my.GO.table <- Term(my.GO)
my.GO.table
t <- as.matrix(my.GO.table)
```

?seq()

write.table(t, file="tf2cmbr_wtcmbr_DE1_sigonly_ALL_GOmerge.txt")

library(rmarkdown)
